Running simulations of MultipleContactNeutralMigrat.nlogo

### 2024-09-25 RunSims.Rmd
Updated to submit revision 1

mdl1 %>%  #filter(prob_frag==0.4) %>%
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  ) 
ggsave("Figures/Species_Habitat_Dispersal_Lambda_pf_regular.png",width=8,height=6,units="in",dpi=600)

ggsave("Figures/Shannon_Habitat_Dispersal_Lambda_pf_regular.png",width=8,height=6,units="in",dpi=600)

#
# Number of species by mean_patch size 
# 
mdl1 %>%  
  ggplot(aes(x = mean_patch_mean, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Mean Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

@@

#
# shannon_diversity by mean_patch size 
# 
mdl1  %>% #filter(birds_dispersal_distance %in% c(1.1,1.5,3)) %>%
  ggplot(aes(x = mean_patch_mean, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Mean Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Shannon_MeanPatch_Dispersal_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

@@

```{r SLOSS_lambda14_pf48_block,echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=TRUE}

@@

#
# Number of species by max_patch size 
# 
mdl1 %>%  
  ggplot(aes(x = mean_patch_mean, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Mean Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

@@

#
# shannon_diversity by mean_patch size 
# 
mdl1 %>%  
  ggplot(aes(x = mean_patch_mean, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Mean Patch Size") +  ylab("Shannon Diversity") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

@@

## Simulations Lambda = 1-4 / Regular patterns - Hierarchical communities

* Initial conditions: migration from the regional community and after the area is filled of individuals, then 60% of the area degraded with regular patches (t= 200 for lambda=4 )

```{r Hierarchical_SLOSS_lambda14_simulations_regular,echo=FALSE,message=FALSE,warning=FALSE,eval=FALSE}

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="Hierarchical_pf06_hps3-61_dd1-3_brb1-4_regular",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path","find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "prob-frag" =  0.6,
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"regular\"",
                                             "birds-behavior" = "\"Hierarchical\"",
                                             "replacement-rate" = 0.3
                                             ))

## Read Simulations hierarchical regular Patterns

```{r readSimulationsHierarchicalRegular, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
# Read previous simulations
#
if( file.exists("Simulations/sloss_sim_ff.rds")) {

# Read netlogo simulations and 
# Convert the list of mean_free_path to degraded_mfp and non_degraded_mfp
#
mdl <- read_sloss_simul(outpath,"Hierarchical_pf06_hps3-61_dd1-3_brb1-4_regular_ff.csv")

@@

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="Hierarchical_pf04-08_hps3-61_dd1-3_brb1-4_regular",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path","find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4)),
                                             "prob-frag" =  list(values=c(0.4,0.8))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"regular\"",
                                             "birds-behavior" = "\"Hierarchical\"",
                                             "replacement-rate" = 0.3
                                             ))

@@

@@

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="Hierarchical_pf04-08_hps3-61_dd1-3_brb1-4_block",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path","find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4)),
                                             "prob-frag" =  list(values=c(0.4,0.6,0.8))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"random block\"",
                                             "birds-behavior" = "\"Hierarchical\"",
                                             "replacement-rate" = 0.3
                                             ))

@@

@@

mdl1 %>% 
  ggplot(aes(x=habitat_patch_size, y=calc_number_of_species_mean, color=birds_dispersal_distance)) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds))) +
  geom_ribbon(
    aes(
      ymin = calc_number_of_species_ql,
      ymax = calc_number_of_species_qh,
      fill = birds_dispersal_distance
    ),
    alpha = 0.3,
    colour = NA,
    show.legend = FALSE

  ) +
  scale_color_viridis_c(guide = FALSE) + 
  scale_fill_viridis_c() +
  facet_grid(birds_dispersal_distance ~ birth_rate_birds) + 
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species")

mdl1 %>%  #filter(prob_frag==0.4) %>%
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Hierarchical_Species_Dispersal_pf_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

ggsave("Figures/Hierarchical_Shannon_Dispersal_pf_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

@@

mdl1 %>% 
  ggplot(aes(x=habitat_patch_size, y=calc_number_of_species_mean, color=birds_dispersal_distance)) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds))) +
  geom_ribbon(
    aes(
      ymin = calc_number_of_species_ql,
      ymax = calc_number_of_species_qh,
      fill = birds_dispersal_distance
    ),
    alpha = 0.3,
    colour = NA,
    show.legend = FALSE

  ) +
  scale_color_viridis_c(guide = FALSE) + 
  scale_fill_viridis_c() +
  facet_grid(birds_dispersal_distance ~ birth_rate_birds) + 
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species")

mdl1 %>%  #filter(prob_frag==0.4) %>%
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Hierarchical_Species_Dispersal_pf_Lambda_block.png",width=8,height=6,units="in",dpi=600)

ggsave("Figures/Hierarchical_Shannon_Dispersal_pf_Lambda_block.png",width=8,height=6,units="in",dpi=600)

@@

* Initial conditions: migration from the regional community and after the area is filled of individuals, then 60% of the area degraded with regular patches (t= 200 for lambda=4 )

@@

```{r Selection_SLOSS_lambda14_pf48_block,echo=FALSE,message=FALSE,warning=FALSE,eval=FALSE}

>>>>

mdl1 %>%  filter(prob_frag==0.6) %>%
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  #facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  ) 
ggsave("Figures/Species_Habitat_Dispersal_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

# Shannon-Diversity  
#
mdl1 %>%  filter(prob_frag==0.6) %>%
  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  #facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Shannon_Habitat_Dispersal_Lambda_regular.png",width=8,height=6,units="in",dpi=600)

#
# Number of species by mean_patch size 
# 
mdl1 %>%  
  ggplot(aes(x = mean_patch_mean, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance") + 
  #,title = "Clasical neutral model with regular habitat degradation") +
  theme_bw() + xlab("Mean Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

@@

#
# shannon_diversity by mean_patch size 
# 
mdl1  %>% #filter(birds_dispersal_distance %in% c(1.1,1.5,3)) %>%
  ggplot(aes(x = mean_patch_mean, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance",
       title = "Clasical neutral model with regular habitat degradation") +
  theme_bw() + xlab("Mean Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Shannon_MeanPatch_Dispersal_Lambda_pf_regular.png",width=8,height=6,units="in",dpi=600)

@@

```{r SLOSS_lambda14_pf48_block,echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}

@@

#
# Number of species by max_patch size 
# 
mdl1 %>%  
  ggplot(aes(x = mean_patch_mean, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance"
       #,title = "Clasical neutral model with random block habitat degradation"
       ) +
  theme_bw() + xlab("Mean Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

@@

#
# shannon_diversity by mean_patch size 
# 
mdl1 %>%  
  ggplot(aes(x = mean_patch_mean, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance",
       title = "Clasical neutral model with random block habitat degradation") +
  theme_bw() + xlab("Mean Patch Size") +  ylab("Shannon Diversity") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

@@

@@

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="Hierarchical_pf04-08_hps3-61_dd1-3_brb1-4_regular",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path","find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4)),
                                             "prob-frag" =  list(values=c(0.4,0.6,0.8))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "Deforestation-at-time" = 600,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"regular\"",
                                             "birds-behavior" = "\"Hierarchical\"",
                                             "replacement-rate" = 0.3
                                             ))

@@

mdl %>% distinct(prob_frag,deforestation_type,birds_behavior)

sloss_sim %>% distinct(prob_frag,deforestation_type,birds_behavior) %>% arrange(prob_frag,deforestation_type,birds_behavior)

@@

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
# hps = habitat patch size
# dd = dispersal distance 
# brb = bird rate birds 
nl@experiment <- experiment(expname="Hierarchical_pf04-08_hps3-61_dd1-3_brb1-4_block",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path","find-cluster-sizes"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61)),
                                               "birth-rate-birds" = list(values=c(1.7, 2, 3, 4)),
                                             "prob-frag" =  list(values=c(0.4,0.6,0.8))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.0001,
                                             "Video" = "false",
                                             "Deforestation-at-time" = 600,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"random block\"",
                                             "birds-behavior" = "\"Hierarchical\"",
                                             "replacement-rate" = 0.3
                                             ))

@@

sloss_sim %>% distinct(prob_frag,deforestation_type,birds_behavior) %>% arrange(prob_frag,deforestation_type,birds_behavior)

@@

mdl1 %>%
  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance",
       title = "Competitive hierarchical model with regular habitat degradation") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Hierarchical_Species_Dispersal_Lambda_pf_regular.png",width=8,height=6,units="in",dpi=600)

# Shannon-Diversity  
#
mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap(~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance",
       title = "Competitive hierarchical model with regular habitat degradation") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Hierarchical_Shannon_Dispersal_Lambda_pf_regular.png",width=8,height=6,units="in",dpi=600)

#
#
#

mdl1 %>%
  ggplot(aes(x = mean_patch_mean, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance",
       title = "Competitive hierarchical model with regular habitat degradation") +
  theme_bw() + xlab("Mean Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Hierarchical_MeanPatch_Species_Dispersal_Lambda_pf_regular.png",width=8,height=6,units="in",dpi=600)

# Shannon-Diversity  
#
mdl1 %>%  
  ggplot(aes(x = mean_patch_mean, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap(~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance",
       title = "Competitive hierarchical model with regular habitat degradation") +
  theme_bw() + xlab("Mean Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Hierarchical_MeanPatch_Shannon_Dispersal_Lambda_pf_regular.png",width=8,height=6,units="in",dpi=600)

@@

mdl1 %>%  
#  ggplot(aes(x = habitat_patch_size, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  ggplot(aes(x = mean_patch_mean, y = calc_number_of_species_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_number_of_species_ql, ymax = calc_number_of_species_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap( ~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance",
       title = "Competitive hierarchical model with random block habitat degradation") +
  theme_bw() + xlab("Mean Patch Size") + ylab("Number of species") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Hierarchical_MeanPatch_Species_Dispersal_Lambda_pf_block.png",width=8,height=6,units="in",dpi=600)

# Shannon-Diversity  
#
mdl1 %>%  
#  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  ggplot(aes(x = mean_patch_mean, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.2,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  #facet_wrap(~ birth_rate_birds, ncol = 4) + 
  facet_grid(prob_frag ~ birth_rate_birds) +
  labs(color = "Dispersal\n distance",
       title = "Competitive hierarchical model with random block habitat degradation") +
  theme_bw() + xlab("Mean Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

ggsave("Figures/Hierarchical_MeanPatch_Shannon_Dispersal_Lambda_pf_block.png",width=8,height=6,units="in",dpi=600)

@@

* Initial conditions: migration from the regional community and after the area is filled of individuals, then 60% of the area degraded with regular patches (t= 600 )

@@

```{r Selection_SLOSS_lambda14_pf48_block,echo=FALSE,message=FALSE,warning=FALSE,eval=TRUE}
